The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/glossary.rmd
gloss
rm metric interpretations to glossay

**Spatial network**: Networks of locations, which be linked with social networks of animals that move between the locations (Silk et al. 2018.

>>>>

**Spatial network**: Networks of locations, which be linked with social networks of animals that move between the locations (Silk et al. 2018).

<!--
## Each metric's interpretation
* Degree: the number of direct connections an individual has to other individuals in the network. High degree = connected to many indviduals in a single layer. Low degree = not connected to many individuals in a single layer.

* Multidegree: sum of degree across layers. High multidegree = connected to many
individuals across layers. Low multidegree = not connected to many individuals
across layers.

* Degree deviation: standard **[??]** deviation of degree across layers. High degree deviation =
large difference between degree for an individual across layers. Low degree
deviation = individuals are similarly connected across layers.

* Graph strength: the sum of all the edge weights directly connected to an actor, sometimes called weigthed degree. High graph strength = highly social, connected to many individuals and/or having stronger, high-valued connections between individuals. Low graph strength = not very social, connected to few individuals and/or having weak, low-valued connections between individuals. Not summed in this case across layers.

* Neighbours: number of unique individuals adjacent to each actor. Considered in
a single layer, this is equal to the degree.

* Neighbourhood: number of unique individuals across all layers. High
neighbourhood = a high number of unique individuals connected to an actor. Low
neighbourhood = a low number of unique individuals connected to an actor.

* Relevance: layer centric metric, corresponding to the number of neighbours on a
layer divided by the total neighbourhood for each actor. High relevance = the layer is highly relevant to the individuals connections. A low
relevance means this layer does not contribute many neighbours to an individuals
overall neighbourhood.

* Connective redundancy: the total multilayer neighbourhood divided by the
multidegree. High connective redundancy indicates a multilayer network that has
many repeated edges across layers between an actor and its neighbours. Low
connective redundancy indicates that each layer is important for preserving all
social ties.

* Layer similarity: how similar each layer is (Brodka 2018). Pearson's
correlation coefficient of degree vectors for each layer, comparing each
landcover across seasons.

-->
